Comparing vector-based and ACT-R memory models of tag retrieval:\protect\\User-customized hashtag/tag prediction on Twitter and StackOverflow

### 2014-08-01 writeups/dissertation/dissertation.tex
foo

\usepackage{xfrac}
\usepackage{textcomp}
\usepackage[american]{babel}
\usepackage[utf8]{inputenc}

@@

>>>>

\usepackage[nodayofweek]{datetime}% http://ctan.org/pkg/datetime
\usepackage{xfrac}
\usepackage{textcomp}
\usepackage[american]{babel}
\usepackage[utf8]{inputenc}

@@

\def\committee{
  Joseph R. Cavallaro, Chair \\
  Professor of Electrical and Computer Engineering and Computer Science \and
  Behnaam Aazhang \\
  J.S. Abercrombie Professor of Electrical and Computer Engineering \and
  Scott Rixner\\
  Associate Professor of Electrical and Computer Engineering and Computer Science \and
  Ashutosh Sabharwal\\
  Assistant Professor of Electrical and Computer Engineering \\
}

% Replace the title page in the apa6 style sheet with the title page from the Rice template
% The title page style was taken from Rice University LaTeX PhD template: http://scholarship.rice.edu/handle/1911/21747
% The following code for the abstract page was taken from the apa6 \maketitle command.
\makeatletter
\def\maketitle{
  \begin{titlepage}
    \singlespacing
    \null
    \setcounter{page}{1}
    \vfill
    \vbox to 0pt{\vss\vbox to 8.75in{\parskip 0pt \parindent 0pt\centering
      {\large \uppercase\expandafter{Rice University} \par} \vskip 0pt plus 3fil
      {\Large \bf \@title \par} \vskip 0pt plus 1.3fil
      {\large by \par} \vskip 0pt plus 1fil
      {\large \bf \@author \par} \vskip 0pt plus 3fil
      {\large \sc A Thesis Submitted \\
	in Partial Fulfillment of the \\
      Requirements for the Degree \par} \vskip 0pt plus 1.1fil
      {\large \bf Doctor of Philosophy \par} \vskip 0pt plus 4.5fil
      \begingroup
      \leftskip .5\textwidth \rightskip 0pt plus 1fil
      {\sc Approved, Thesis Committee: \par} \vskip 2.5em
      \moveright\leftskip\vbox{\hrule width \leftskip}
      \def\and{\par \vskip 2.25em minus 1em\moveright\leftskip\vbox{\hrule width \leftskip}}
      \committee
      \par \endgroup
      \vskip 0pt plus 2fil
    {\large Houston, TX \par} \vskip 0pt plus .8fil
    {\large \monthnameenglish, \number\year \par}
  }}
  \doublespacing
  \newpage
  %BDB\hyphenpenalty 10000
  \fussy
  \@ifundefined{@abstract}{}{%
    \section{\normalfont\normalsize\abstractname}% BDB
    \noindent\@abstract\par% BDB
    \@ifundefined{@keywords}{}{%
      \setlength{\parindent}{0.4in}% BDB
      \indent\textit{\keywordname:} \@keywords%
    }%
    \newpage
  }
  \@ifundefined{def@donotrepeattitle}{
    \section{\protect\normalfont{\@title}}
  }{}%
  \raggedright%
  \setlength{\parindent}{0.4in}%
\end{titlepage}}
\makeatother
